### 2014-12-08 d-sep_test.Rmd
language edit

Combine the p-values into the *C*-statistic
```{r calculate C statistic}
ln_pvalues <- log(pvalues)
C_stat <- -2*sum(ln_pvalues)
```
I would like to figure out how to calculate the chi-square cumulative probability based on the degrees of freedom and *C*-statistic, a la this [website](http://stattrek.com/online-calculator/chi-square.aspx)

>>>>

Combine the p-values into the *C*-statistic
```{r calculate C statistic}
ln_pvalues <- log(pvalues)
C_stat <- -2*sum(ln_pvalues)
```
I would like to learn how to calculate the chi-square cumulative probability based on the degrees of freedom and *C*-statistic, a la this [website](http://stattrek.com/online-calculator/chi-square.aspx)
